Regular singular Volterra equations on complex domains

### 2023-08-08 reg-sing-volterra.tex
Revise proof of thm:general_volterra

% operator under consideration
\newcommand{\volterra}{\mathcal{V}}
\newcommand{\hardpart}{\mathcal{V}_0}
\newcommand{\softpart}{\mathcal{V}_\star}
\newcommand{\hardker}{k_0}
\newcommand{\softker}{k_\star}
\newcommand{\solproto}{f_0}
\newcommand{\solptb}{f_\star}

@@

We'll prove this result in Section~\ref{sec:proto-construction-regularity}, Proposition~\ref{prop:asymptotic at infinity}.
\begin{thm}\label{thm:general_volterra}
In the perturbed operator $\volterra = \hardpart +\softpart$ from Section~\ref{setting}, suppose the prototypical part $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}}, \eqref{cond:slow}, and \eqref{cond:diag-basic} from Section~\ref{setting:basic}, and the perturbation $\softpart$ satisfies Condition \eqref{cond:eps-lambda} from Section~\ref{setting:perturbed}. Then the Volterra equation
\[f = \volterra f\]
has a unique solution $f$ in the affine subspace
\[ f_0 + \singexpalg{\tau-1+\epsilon}(\Omega) \]
of the function space $\singexpalg{\tau-1}(\Omega)$ defined in Section~\ref{fn-spaces}. Here, $f_0$ is the prototype solution \eqref{eqn:test_solution} from Theorems \ref{thm:basic_volterra}--\ref{thm:proto-growth}, which belongs to the function space $\singexp{\tau-1}{\lambda_0}(\Omega)$. For any $\rho > \tau$, the uniqueness of the solution still holds in the larger affine subspace $f_0 + \singexpalg{\rho-1}(\Omega)$.
\textcolor{RoyalBlue}{Assume $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}, \eqref{cond:slow}} and {\em \eqref{cond:diag-basic}} from Section \ref{setting:basic}. Assume $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}} from Section \ref{setting:perturbed}. Then the Volterra equation 
\[f = \left[ \hardpart + \softpart \right] f\]
admits a unique solution in the affine subspace
\[ f_0 + \singexpalg{\tau-1+\epsilon}(\Omega) \]
of the function space $\singexpalg{\tau-1}(\Omega)$, defined in Section~\ref{fn-spaces}. The function $f_0$ is the prototypical solution of \eqref{eqn:test_solution} and it belongs to the function space $\singexp{\tau-1}{\lambda_0}(\Omega)$.}
\end{thm}
\textcolor{RoyalBlue}{We'll prove this result in Sections~\ref{sec:existence and uniqueness}: using Proposition \ref{prop:smoothing} we show that $\softpart$ maps the prototype solution into a more regular function space. Then the result follows as a consequence of Lemma \ref{lem:perturbed_volterra}.}\par
%--------
This result will follow from a more general result about inhomogeneous equations.
\begin{lemma}\label{lem:perturbed_volterra}
In the perturbed operator $\volterra = \hardpart +\softpart$ from Section~\ref{setting}, suppose the prototypical part $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \eqref{cond:diag-basic} \textcolor{magenta}{[I don't think we actually use \texttt{cond:slow}]} from Section~\ref{setting:basic}, and the perturbation $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}} from Section~\ref{setting:perturbed}. Suppose we're also given a function $g$, which for some $\rho > \tau$ belongs to the space $\singexpalg{\rho-1}(\Omega)$ defined in Section~\ref{fn-spaces}. Then the inhomogeneous Volterra equation
\[ f = \volterra f + g, \]
has a unique solution $f$ in the space $\singexpalg{\rho-1}(\Omega)$.

@@

\subsection{Continuous inclusions between different $\singexp{\sigma}{\Lambda}(\Omega)$}\label{sec:inclusions}
\begin{prop}\label{prop:exp-inclus}
If $\Lambda'\leq\Lambda$, the inclusion map $\singexp{\sigma}{\Lambda'}(\Omega)\hookrightarrow \singexp{\sigma}{\Lambda}(\Omega)$ is continuous.
\end{prop}
\begin{proof}
By definition,
\[ \|f\|_{\sigma,\Lambda}=\sup_{\Omega} |\zeta|^{-\sigma}\,e^{-\Lambda |\zeta|}\, |f|. \]
The norm $\|\cdot\|_{\sigma, \Lambda'}$ is designed to give $|f| \le |\zeta|^\sigma\,e^{\Lambda'|\zeta|}\,\|f\|_{\sigma, \Lambda'}$, which tells us that
\begin{align*}
\|f\|_{\sigma,\Lambda} & \leq \sup_{\Omega} |\zeta|^{-\sigma}\,e^{-\Lambda |\zeta|}\,|\zeta|^\sigma\,e^{\Lambda'|\zeta|}\,\|f\|_{\sigma, \Lambda'}\\
&=\sup_{\Omega} e^{-(\Lambda-\Lambda') |\zeta|}\,\|f\|_{\sigma, \Lambda'}\\
&\leq \|f\|_{\sigma,\Lambda'}.
\end{align*}
In the last step, we use the assumption that $\Lambda' \le \Lambda$.
\end{proof}
As we mentioned in Section~\ref{sec:fn-space-defs}, one might describe $\singexp{0}{\Lambda}(\domain)$ as the space of functions on $\domain$ which are uniformly of exponential type $\Lambda$. Taking the union of these spaces over all $\Lambda \in \R$, we get the space $\singexpalg{0}$ that contains all functions of exponential type. Having continuous inclusions between the subspaces $\singexp{0}{\Lambda}(\domain)$ as $\Lambda$ increases, we can give $\singexpalg{0}$ a meaningful topology: the finest topology that makes all the inclusions $\singexp{0}{\Lambda}(\domain) \hookrightarrow \singexpalg{0}$ continuous.\footnote{In category-theoretic language, $\singexpalg{0}$ is the limit of the family $\singexp{0}{\Lambda}(\domain)$.}
\begin{prop}
    If $\Lambda'<\Lambda$ and $\sigma'>\sigma$, the inclusion map $\singexp{\sigma'}{\Lambda'}(\Omega)\hookrightarrow \singexp{\sigma}{\Lambda}(\Omega)$ is continuous.
\end{prop}

\begin{proof}
By definition,
\begin{align*}
\|f\|_{\sigma,\Lambda}&=\sup_{\Omega} |\zeta|^{-\sigma}  e^{-\Lambda |\zeta|} |f|\\
&= \sup_{\Omega} |\zeta|^{\sigma'-\sigma}\,|\zeta|^{-\sigma'}\,e^{-\Lambda'|\zeta|}\,  e^{-(\Lambda-\Lambda') |\zeta|} \, |f|.
\end{align*}
The function $|\zeta|^{\sigma'-\sigma}\,  e^{-(\Lambda-\Lambda') |\zeta|}$ is bounded near $\zeta = 0$ because the power of $|\zeta|$ is positive, and it's bounded far from $\zeta = 0$ thanks to the decaying exponential. Hence,
\begin{align*}
\|f\|_{\sigma,\Lambda}&\leq C\sup_\Omega  |\zeta|^{-\sigma'}\, e^{-\Lambda'|\zeta|} \, |f|\\
&=C \|f\|_{\sigma',\Lambda'}
\end{align*}
for $C = \sup_{\Omega}  |\zeta|^{\sigma'-\sigma}\,  e^{-(\Lambda-\Lambda') |\zeta|}$.
\end{proof}

@@

In this Section, we show that, under Condition \eqref{cond:eps-lambda}, the smoothing effect of the operator $\softpart$ regularizes the prototype solution $f_0$: recall from Section \ref{sec:asymptotics} that $f_0\in\singexp{\tau-1}{\lambda_0}(\Omega)$, then we'll show $\softpart f_0 \in\singexp{\tau-1+\epsilon}{\Lambda}(\Omega)$ for $\Lambda\geq \lambda_\Delta$. This is a consequence of a more general result (see Proposition \ref{prop:smoothing}), namely that $\softpart$ regularises functions in $\singexp{\sigma}{\Lambda}(\Omega)$ which are not too singular at $\zeta=0$.

@@

To see that the fixed point is still unique in the bigger space $\singexpalg{\rho-1}(\Omega)$, first recall from Proposition~\ref{prop:exp-inclus} that we have inclusions $\singexp{\rho-1}{\Lambda'}(\Omega) \hookrightarrow \singexp{\rho-1}{\Lambda}(\Omega)$ for all $\Lambda' \le \Lambda$. Any fixed point in $\singexp{\rho-1}{\Lambda'}(\Omega)$ must map to the unique fixed point in $\singexp{\rho-1}{\Lambda}(\Omega)$ under this inclusion. Next, observe that for any $\Lambda'' \ge \Lambda$, the map $f \mapsto \volterra f + g$ is also a contraction of $\singexp{\rho-1}{\Lambda''}(\Omega)$. The inclusion $\singexp{\rho-1}{\Lambda}(\Omega) \hookrightarrow \singexp{\rho-1}{\Lambda''}(\Omega)$ must send the unique fixed point in the smaller space to the unique fixed point in the larger one. Together, these arguments show that the fixed point is unique in $\singexpalg{\rho-1}(\Omega)$.
\end{proof}
\begin{proof}[Proof of Theorem~\ref{thm:general_volterra}]
%\textcolor{magenta}{[we have to change the definition of $\hardker$ in \S \ref{setting:basic} in $-\frac{q(a')}{p(a)}$.]}
By Theorem \ref{thm:basic_volterra} and \ref{thm:proto-growth} (proved in Section \ref{sec:construction}), there exists a function $f_0\in \singexp{\tau-1}{\lambda_0}(\Omega)$ such that $\hardpart f_0= f_0$. Hence we can solve the Volterra equation

>>>>

% operator under consideration
\newcommand{\volterra}{\mathcal{V}}
\newcommand{\hardpart}{\mathcal{V}_0}
\newcommand{\softpart}{\mathcal{V}_\star}
\newcommand{\hardker}{k_0}
\newcommand{\softker}{k_\star}
\newcommand{\solwhole}{f}
\newcommand{\solproto}{f_0}
\newcommand{\solptb}{f_\star}

@@

We'll prove this result in Section~\ref{sec:proto-construction-regularity}, Proposition~\ref{prop:asymptotic at infinity}.
\begin{thm}\label{thm:general_volterra}
In the perturbed operator $\volterra = \hardpart +\softpart$ from Section~\ref{setting}, suppose the prototypical part $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}}, \eqref{cond:slow}, and \eqref{cond:diag-basic} from Section~\ref{setting:basic}, and the perturbation $\softpart$ satisfies Condition \eqref{cond:eps-lambda} from Section~\ref{setting:perturbed}. Then the Volterra equation
\[f = \volterra f\]
has a unique solution $f$ in the affine subspace
\[ f_0 + \singexpalg{\tau-1+\epsilon}(\Omega) \]
of the function space $\singexpalg{\tau-1}(\Omega)$ defined in Section~\ref{fn-spaces}. Here, $f_0$ is the prototype solution \eqref{eqn:test_solution} from Theorems \ref{thm:basic_volterra}--\ref{thm:proto-growth}, which belongs to the function space $\singexp{\tau-1}{\lambda_0}(\Omega)$.

For any $\rho > \tau$, the uniqueness of the solution still holds in $f_0 + \singexpalg{\rho-1}(\Omega)$. In other words, lowering $\rho$ into $(\tau, \tau+\epsilon)$ to allow a sharper singularity won't reveal any more solutions, and raising $\rho$ too high to admit the solution found in $f_0 + \singexpalg{\tau-1+\epsilon}(\Omega)$ will leave no solution at all.
\par\textcolor{RoyalBlue}{Assume $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}, \eqref{cond:slow}} and {\em \eqref{cond:diag-basic}} from Section \ref{setting:basic}. Assume $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}} from Section \ref{setting:perturbed}. Then the Volterra equation 
\[f = \left[ \hardpart + \softpart \right] f\]
admits a unique solution in the affine subspace
\[ f_0 + \singexpalg{\tau-1+\epsilon}(\Omega) \]
of the function space $\singexpalg{\tau-1}(\Omega)$, defined in Section~\ref{fn-spaces}. The function $f_0$ is the prototypical solution of \eqref{eqn:test_solution} and it belongs to the function space $\singexp{\tau-1}{\lambda_0}(\Omega)$.}
\end{thm}
\textcolor{RoyalBlue}{We'll prove this result in Sections~\ref{sec:existence and uniqueness}: using Proposition \ref{prop:smoothing} we show that $\softpart$ maps the prototype solution into a more regular function space. Then the result follows as a consequence of Lemma \ref{lem:perturbed_volterra}.}\par
%--------
This result will follow from a more general result about inhomogeneous equations.
\begin{lemma}\label{lem:perturbed_volterra}
In the perturbed operator $\volterra = \hardpart +\softpart$ from Section~\ref{setting}, suppose the prototypical part $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \eqref{cond:diag-basic} \textcolor{magenta}{[I don't think we actually use \texttt{cond:slow}]} from Section~\ref{setting:basic}, and the perturbation $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}} from Section~\ref{setting:perturbed}. Suppose we're also given a function $g$, which for some $\rho > \tau$ belongs to the space $\singexpalg{\rho-1}(\Omega)$ defined in Section~\ref{fn-spaces}. Then the inhomogeneous Volterra equation
\[ f = \volterra f + g, \]
has a unique solution $f$ in the space $\singexpalg{\rho-1}(\Omega)$.

@@

\subsection{Continuous inclusions between different $\singexp{\sigma}{\Lambda}(\Omega)$}\label{sec:inclusions}
\begin{prop}\label{prop:inclus-ge-exp}
If $\Lambda'\leq\Lambda$, the inclusion map $\singexp{\sigma}{\Lambda'}(\Omega)\hookrightarrow \singexp{\sigma}{\Lambda}(\Omega)$ is continuous.
\end{prop}
\begin{proof}
By definition,
\[ \|f\|_{\sigma,\Lambda}=\sup_{\Omega} |\zeta|^{-\sigma}\,e^{-\Lambda |\zeta|}\, |f|. \]
The norm $\|\cdot\|_{\sigma, \Lambda'}$ is designed to give $|f| \le |\zeta|^\sigma\,e^{\Lambda'|\zeta|}\,\|f\|_{\sigma, \Lambda'}$, which tells us that
\|f\|_{\sigma,\Lambda} & \leq \sup_{\Omega} |\zeta|^{-\sigma}\,e^{-\Lambda |\zeta|}\,|\zeta|^\sigma\,e^{\Lambda'|\zeta|}\,\|f\|_{\sigma, \Lambda'}\\
&=\sup_{\Omega} e^{-(\Lambda-\Lambda') |\zeta|}\,\|f\|_{\sigma, \Lambda'}\\
&\leq \|f\|_{\sigma,\Lambda'}.
In the last step, we use the assumption that $\Lambda' \le \Lambda$.
As we mentioned in Section~\ref{sec:fn-space-defs}, one might describe $\singexp{0}{\Lambda}(\domain)$ as the space of functions on $\domain$ which are uniformly of exponential type $\Lambda$. Taking the union of these spaces over all $\Lambda \in \R$, we get the space $\singexpalg{0}$ that contains all functions of exponential type. Having continuous inclusions between the subspaces $\singexp{0}{\Lambda}(\domain)$ as $\Lambda$ increases, we can give $\singexpalg{0}$ a meaningful topology: the finest topology that makes all the inclusions $\singexp{0}{\Lambda}(\domain) \hookrightarrow \singexpalg{0}$ continuous.\footnote{In category-theoretic language, $\singexpalg{0}$ is the limit of the family $\singexp{0}{\Lambda}(\domain)$.}
\begin{prop}\label{prop:inclus-lt-pow-gt-exp}
If $\sigma'>\sigma$ and $\Lambda'<\Lambda$, the inclusion map $\singexp{\sigma'}{\Lambda'}(\Omega)\hookrightarrow \singexp{\sigma}{\Lambda}(\Omega)$ is continuous.
\end{prop}
\begin{proof}
By definition,
\|f\|_{\sigma,\Lambda}&=\sup_{\Omega} |\zeta|^{-\sigma}  e^{-\Lambda |\zeta|} |f|\\
&= \sup_{\Omega} |\zeta|^{\sigma'-\sigma}\,|\zeta|^{-\sigma'}\,e^{-\Lambda'|\zeta|}\,  e^{-(\Lambda-\Lambda') |\zeta|} \, |f|.
The function $|\zeta|^{\sigma'-\sigma}\,  e^{-(\Lambda-\Lambda') |\zeta|}$ is bounded near $\zeta = 0$ because the power of $|\zeta|$ is positive, and it's bounded far from $\zeta = 0$ thanks to the decaying exponential. Hence,
\|f\|_{\sigma,\Lambda}&\leq C\sup_\Omega  |\zeta|^{-\sigma'}\, e^{-\Lambda'|\zeta|} \, |f|\\
&=C \|f\|_{\sigma',\Lambda'}
for $C = \sup_{\Omega}  |\zeta|^{\sigma'-\sigma}\,  e^{-(\Lambda-\Lambda') |\zeta|}$.
\begin{prop}\label{prop:inclus-lt-pow-alg}
When $\sigma' > \sigma$, there's a continuous inclusion $\singexpalg{\sigma'}(\Omega)\hookrightarrow \singexpalg{\sigma}(\Omega)$.
\end{prop}
\begin{proof}
For each $\Lambda'$, we can get a continuous inclusion $\singexp{\sigma'}{\Lambda'}(\Omega) \hookrightarrow \singexpalg{\sigma}(\Omega)$ by choosing some $\Lambda > \Lambda'$ and composing the continuous inclusion $\singexp{\sigma'}{\Lambda'}(\Omega) \hookrightarrow \singexp{\sigma}{\Lambda}(\Omega)$ given by Proposition~\ref{prop:inclus-lt-pow-gt-exp} with the continuous inclusion $\singexp{\sigma}{\Lambda}(\Omega) \hookrightarrow \singexpalg{\sigma}(\Omega)$ that we get by definition. For any $\Lambda'' < \Lambda'$, the inclusions $\singexp{\sigma'}{\Lambda''}(\Omega) \hookrightarrow \singexpalg{\sigma}(\Omega)$ and $\singexp{\sigma'}{\Lambda'}(\Omega) \hookrightarrow \singexpalg{\sigma}(\Omega)$ constructed above automatically commute with the inclusion $\singexp{\sigma'}{\Lambda''}(\Omega) \hookrightarrow \singexp{\sigma'}{\Lambda'}(\Omega)$ given by Proposition~\ref{prop:inclus-ge-exp}, because we're ultimately working in the vector space of holomorphic functions on $\Omega$. Because of how the topology on $\singexpalg{\sigma'}(\Omega)$ is defined, this gives us the desired continuous inclusion $\singexpalg{\sigma'}(\Omega)\hookrightarrow \singexpalg{\sigma}(\Omega)$.

@@

\textcolor{orange}{[Read through and revise]} In this Section, we show that, under Condition \eqref{cond:eps-lambda}, the smoothing effect of the operator $\softpart$ regularizes the prototype solution $f_0$: recall from Section \ref{sec:asymptotics} that $f_0\in\singexp{\tau-1}{\lambda_0}(\Omega)$, then we'll show $\softpart f_0 \in\singexp{\tau-1+\epsilon}{\Lambda}(\Omega)$ for $\Lambda\geq \lambda_\Delta$. This is a consequence of a more general result (see Proposition \ref{prop:smoothing}), namely that $\softpart$ regularises functions in $\singexp{\sigma}{\Lambda}(\Omega)$ which are not too singular at $\zeta=0$.

@@

To see that the fixed point is still unique in the bigger space $\singexpalg{\rho-1}(\Omega)$, first recall from Proposition~\ref{prop:inclus-ge-exp} that we have inclusions $\singexp{\rho-1}{\Lambda'}(\Omega) \hookrightarrow \singexp{\rho-1}{\Lambda}(\Omega)$ for all $\Lambda' \le \Lambda$. Any fixed point in $\singexp{\rho-1}{\Lambda'}(\Omega)$ must map to the unique fixed point in $\singexp{\rho-1}{\Lambda}(\Omega)$ under this inclusion. Next, observe that for any $\Lambda'' \ge \Lambda$, the map $f \mapsto \volterra f + g$ is also a contraction of $\singexp{\rho-1}{\Lambda''}(\Omega)$. The inclusion $\singexp{\rho-1}{\Lambda}(\Omega) \hookrightarrow \singexp{\rho-1}{\Lambda''}(\Omega)$ must send the unique fixed point in the smaller space to the unique fixed point in the larger one. Together, these arguments show that the fixed point is unique in $\singexpalg{\rho-1}(\Omega)$.
\end{proof}
\begin{proof}[Proof of Theorem~\ref{thm:general_volterra}]
%\textcolor{magenta}{[we have to change the definition of $\hardker$ in \S \ref{setting:basic} in $-\frac{q(a')}{p(a)}$.]}
Start with the prototype solution $\solproto$ constructed in Theorem~\ref{thm:basic_volterra}, which satisfies the equation
\[ \solproto = \hardpart \solproto. \]
The base point for the construction can be chosen arbitrarily. Under our assumptions about $\volterra$, Theorem~\ref{thm:proto-growth} tells us that $\solproto$ is in $\singexp{\tau-1}{\lambda_0}(\Omega)$. Our goal is to find a perturbation $\solptb \in \singexpalg{\tau-1+\epsilon}(\Omega)$ that makes $\solwhole = \solproto + \solptb$ a solution of
\begin{equation}\label{eqn:orig-homog}
\solwhole = \volterra \solwhole.
\end{equation}
Observing that
\begin{align*}
\volterra \solproto & = \hardpart\solproto + \softpart\solproto \\
& = \solproto + \softpart \solproto,
\end{align*}
we can rewrite the homogeneous equation we're trying to solve as an inhomogeneous equation for $\solptb$:
\begin{align}
\solproto + \solptb & = \volterra\solproto + \volterra\solptb \nonumber \\
& = \solproto + \softpart\solproto + \volterra\solptb \nonumber \\
\solptb & = \softpart\solproto + \volterra\solptb. \label{eqn:equiv-inhomog}
\end{align}
Since we know that $\solproto$ is in $\singexp{\tau-1}{\lambda_0}(\Omega)$, Proposition~\ref{prop:smoothing} tells us that the inhomogeneous term $\softpart\solproto$ is in $\singexp{\tau-1+\epsilon}{\lambda_0}(\Omega)$. Since $\tau+\epsilon > \tau$, and we've made all the necessary assumptions about $\volterra$, Lemma~\ref{lem:perturbed_volterra} guarantees that Equation~\eqref{eqn:equiv-inhomog} has a unique solution $\solptb$ in $\singexpalg{\tau-1+\epsilon}(\Omega)$. Equivalently, Equation~\eqref{eqn:orig-homog} has a unique solution $f$ in $f_0 + \singexpalg{\tau-1+\epsilon}(\Omega)$.

Now, we just want to show that the uniqueness of the solution still holds in $f_0 + \singexpalg{\rho-1}(\Omega)$ for any $\rho > \tau$.

First, suppose $\rho \in (\tau, \tau+\epsilon)$. In this case, we can use the inclusion $\singexpalg{\tau-1+\epsilon}(\Omega) \hookrightarrow \singexpalg{\rho-1}(\Omega)$ given by Proposition~\ref{prop:inclus-lt-pow-alg} to see that the inhomogeneous term $\softpart\solproto$ is in $\singexpalg{\rho-1}(\Omega)$. Lemma~\ref{lem:perturbed_volterra} then guarantees that Equation~\eqref{eqn:equiv-inhomog} has a unique solution in $\singexpalg{\rho-1}(\Omega)$---which must be the solution we already found in $\singexpalg{\tau-1+\epsilon}(\Omega)$.

On the other hand, suppose $\rho > \tau+\epsilon$. In this case, Proposition~\ref{prop:inclus-lt-pow-alg} gives an inclusion $\singexpalg{\rho-1}(\Omega) \hookrightarrow \singexpalg{\tau-1+\epsilon}(\Omega)$. Under this inclusion, any solution of Equation~\eqref{eqn:equiv-inhomog} that we might find in $\singexpalg{\rho-1}(\Omega)$ must match the unique solution we found in $\singexpalg{\tau-1+\epsilon}(\Omega)$.

%%the inhomogeneous term $\softpart\solproto$ is still in $\singexpalg{\rho-1}(\Omega)$ by Proposition~\ref{prop:inclus-lt-pow-gt-exp}, so Lemma~\ref{lem:perturbed_volterra} still guarantees that Equation~\eqref{eqn:equiv-inhomog} has a unique solution in $\singexpalg{\rho-1}(\Omega)$---which must be the solution we already found.

\color{RoyalBlue}
By Theorem \ref{thm:basic_volterra} and \ref{thm:proto-growth} (proved in Section \ref{sec:construction}), there exists a function $f_0\in \singexp{\tau-1}{\lambda_0}(\Omega)$ such that $\hardpart f_0= f_0$. Hence we can solve the Volterra equation
